The letter

### 2010-06-30 ltx/PLoS/LaTeX_Manuscript.tex
added some comments

% Please keep the abstract between 250 and 300 words
\section*{Abstract}
This paper presents a framework for creating neural field models from patient-specific or experimental electrophysiological data. The Wilson and Cowen or Amari style neural field equations are used to form a parametric model, where the parameters are estimated from data. To illustrate the estimation framework, data is generated using the neural field equations incorporating modelled sensors, so a comparison can be made between estimated and true parameters. To facilitate state and parameter estimation, we introduce a method to reduce the continuum neural field model, using a basis function decomposition, forming a finite-dimensional state-space model. Spatial frequency analysis methods are introduced for model selection by systematically specifying the basis function configuration required to capture the dominant characteristics of the neural field. The estimation procedure consists of a two-stage iterative algorithm incorporating the unscented Rauch-Tung-Striebel smoother for state estimation and a least squares algorithm for parameter estimation. The results show that it is theoretically possible to reconstruct the neural field and estimate intracortical connectivity and synaptic dynamics with the proposed framework. The results also illustrate the loss of high spatial frequency information as the cost incurred by the model reduction procedure. This framework provides a link between neurophysiological data and theoretical neural field models. This link may lead to greater understanding of cortical dynamics at the mesoscopic and macroscopic scales where diseases such as epilepsy are manifested.

@@

For models to be clinically viable, they must be patient-specific. A possible approach to achieve this would be to fit a general continuum neural field model, like the Wilson and Cohen (WC)~\cite{Wilson1973} or Amari~\cite{Amari1977} models or a neural mass model like the Jansen and Ritt model~\cite{Jansen1995} to patient-specific data. Fitting the neural models to individuals is a highly non-trivial task and, until very recently, has not been reported in the literature.

>>>>

% Please keep the abstract between 250 and 300 words
\section*{Abstract}
This paper presents a framework for creating neural field models from patient-specific or experimental electrophysiological data. The Wilson and Cowen \parham{shouldn't be Cowan?} or Amari style neural field equations are used to form a parametric model, where the parameters are estimated from data. To illustrate the estimation framework, data is generated using the neural field equations incorporating modelled sensors, so a comparison can be made between estimated and true parameters. To facilitate state and parameter estimation, we introduce a method to reduce the continuum neural field model, using a basis function decomposition, forming a finite-dimensional state-space model. Spatial frequency analysis methods are introduced for model selection \parham{ model selection bit should be removed} by systematically specifying the basis function configuration required to capture the dominant characteristics of the neural field. The estimation procedure consists of a two-stage iterative algorithm incorporating the unscented Rauch-Tung-Striebel smoother for state estimation and a least squares algorithm for parameter estimation. The results show that it is theoretically possible to reconstruct the neural field and estimate intracortical connectivity and synaptic dynamics with the proposed framework. The results also illustrate the loss of high spatial frequency information as the cost incurred by the model reduction procedure. This framework provides a link between neurophysiological data and theoretical neural field models. This link may lead to greater understanding of cortical dynamics at the mesoscopic and macroscopic scales where diseases such as epilepsy are manifested.

@@

For models to be clinically viable, they must be patient-specific. A possible approach to achieve this would be to fit a general continuum neural field model, like the Wilson and Cohen \parham{Shouldn't be Cowan?} (WC)~\cite{Wilson1973} or Amari~\cite{Amari1977} models or a neural mass model like the Jansen and Ritt model~\cite{Jansen1995} to patient-specific data. Fitting the neural models to individuals is a highly non-trivial task and, until very recently, has not been reported in the literature.
